Paper_analyses

### 2021-07-26 Paper_Analyses_subj_obje_arousal.Rmd
started working on #2
- created the formats for the plot
- ran additional models using real velocity (with direction) opposed to the speed which is what i had done previously.

timecourse_60bin_result_df %>%
  ggplot(aes(timebins, t_ar))+
  geom_line(size = 1)+
  geom_line(aes(y = t_vl), linetype = "dashed", size = 1)+
  # geom_line(aes(y = t_br), linetype = "dotted", size = 1)+
  geom_line(aes(y = t_ar_vl), linetype = "dotdash", size = 1, color = "red")

@@

>>>>

View(timecourse_60bin_result_df)

timecourse_60bin_result_df %>%
  ggplot(aes(timebins, Estimate_ar))+
  geom_line(size = 1, linetype = 'dotted', color = 1)+
  # geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
  geom_line(aes(y = Estimate_br), size = 1, color = 2)+
  # geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")+
  geom_rect(aes(xmin = 1,
                xmax = 5.89,
                ymin = -2,
                ymax = -2+.1,
                fill = "red", linetype = 'dashed'), alpha = .01)+
  p$graphstyle+
  scale_color_brewer(palette="Dark2")
  scale_color_manual(values=wes_palette(n=3, name="GrandBudapest"))

library(RColorBrewer)

  brewer.pal(4, "Dark2")
  # "#1B9E77" "#D95F02" "#7570B3" "#E7298A"
  # timecourse_60bin_result_df$
  # Estimate_ar, Estimate_ar_vl,Estimate_br. Estimate_v

  timecourse_60bin_result_df %>% 
  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
    subset(!is.na(Estimate))%>%
  ggplot(aes(timebins, Estimate, group = variable, fill = variable, color= variable))+
  geom_line(aes(linetype = variable), size = 1)+
    p$graphstyle+
    scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
  # use correction for significance
    # brighteness
    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_br_adj_TRUE == TRUE]
    annotate(geom = 'rect', 
             xmin = .16,
                xmax = 6,
                ymin = -2,
                ymax = -2+.1,
                fill = "#7570B3", alpha = .5)+

      annotate("text", 
                x = (1+5.4)/2,
                y = ((-2) +(-2+.1))/2,
                label = "brightness") +

    # arousal
    # timecourse_60bin_result_df$p_ar_adj
    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_adj_TRUE == TRUE]
     annotate(geom = 'rect', xmin = 1,
                xmax = 5.89,
                ymin = -2+.1+.1,
                ymax = -2+.1+.1+.1,
                fill = "#1B9E77", alpha = .5)+
        annotate("text", 
                x = (1+5.4)/2,
                y = ((-2+.1+.1) +(-2+.1+.1+.1))/2,
                label = "arousal") +

    # arousal-valence
   # timecourse_60bin_result_df$p_ar_vl_adj
    # timecourse_60bin_result_df$timebins[timecourse_60bin_result_df$p_ar_vl_adj_TRUE == TRUE]
       annotate(geom = 'rect', 
                xmin = 1,
                xmax = 5.4,
                ymin = -2+.1+.1+.1+.1,
                ymax = -2+.1+.1+.1+.1+.1,
                fill = "#D95F02", alpha = .5, label = "text")+
    annotate("text", 
                x = (1+5.4)/2,
                y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2,
                label = "arousal x valence") +
        xlab("Time (s)")+
    ylab("Effect size")+
    xlab("Time (s)")+
    ylab("Effect size")

    # valence - no significance

    # scale_fill_brewer()

?annotate
```

@@

View(timecourse_60bin_result_df_vel)
```

velocity = actual velocity unlike speed (which is what I actually computed above. velocity encodes durection( constriction or dilation)

```{r}
# let's test the interaction term
nbins<- unique(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)
range(tmp.df4_full_stim_downs_jun2021_60bins$timebin_no)

# create and empty dataframe for the timecourse analyses
timecourse_60bin_result_df_vel_dir <- data.frame(timebins= rep(NA, 60), 
                                       Estimate_ar= rep(NA, 60), 
                                       t_ar=rep(NA, 60), 
                                       p_ar=rep(NA, 60),
                                       Estimate_vl= rep(NA, 60), 
                                       t_vl=rep(NA, 60), 
                                       p_vl=rep(NA, 60),
                                       Estimate_br= rep(NA, 60), 
                                       t_br=rep(NA, 60), 
                                       p_br=rep(NA, 60),
                                       Estimate_ar_vl= rep(NA, 60), 
                                       t_ar_vl=rep(NA, 60), 
                                       p_ar_vl=rep(NA, 60),
                                       cov= as.character(rep(NA,60)))

i = 0 # remember to always rezero it
# rm(i,b)

    message(sprintf("$$$$$RUNING lmer %i", nbins[b]))
        lmer_bin_pup  <- lmer(pup_velocity_dir ~ (arousal_c* valence)+Mean_gray_z  +
                                (1 | ssid),
                                # (0 +arousal_c* valence | ssid),
                                # (1|stimIAPS),
                              REML = FALSE,
                      data = subset(tmp.df4_full_stim_downs_jun2021_60bins,
                                    ssid_num< 500&
                                    !is.na(pup_vel_smooth) &
                                    timebin_no == nbins[b]))

        # store results from the simulation
            lmer_bin_pup_summary<- summary(lmer_bin_pup)
            lmer_bin_pup_summary
            # lmer_bin_pup_summary[["coefficients"]][3,1]
            timecourse_60bin_result_df_vel_dir[i,1]<- tmp.df4_full_stim_downs_jun2021_60bins$timerezero3[b] 
            #save the exact value of time bin
            # store arousal (2,parameter)            # first number is term(row), second is column
            timecourse_60bin_result_df_vel_dir[i,2]<-
            lmer_bin_pup_summary[["coefficients"]][2,1] #estimate
            timecourse_60bin_result_df_vel_dir[i,3]<-
              lmer_bin_pup_summary[["coefficients"]][2,4] # t statistic
            timecourse_60bin_result_df_vel_dir[i,4]<-
            lmer_bin_pup_summary[["coefficients"]][2,5] # p value

            timecourse_60bin_result_df_vel_dir[i,5]<-
            lmer_bin_pup_summary[["coefficients"]][3,1] #estimate
            timecourse_60bin_result_df_vel_dir[i,6]<-
              lmer_bin_pup_summary[["coefficients"]][3,4] # t statistic
            timecourse_60bin_result_df_vel_dir[i,7]<-
              lmer_bin_pup_summary[["coefficients"]][3,5] # p value

            # brightness

            timecourse_60bin_result_df_vel_dir[i,8]<-
            lmer_bin_pup_summary[["coefficients"]][4,1] #estimate
            timecourse_60bin_result_df_vel_dir[i,9]<-
              lmer_bin_pup_summary[["coefficients"]][4,4] # t statistic
            timecourse_60bin_result_df_vel_dir[i,10]<-
              lmer_bin_pup_summary[["coefficients"]][4,5] # p value

            timecourse_60bin_result_df_vel_dir[i,11]<-
            lmer_bin_pup_summary[["coefficients"]][5,1] #estimate
            timecourse_60bin_result_df_vel_dir[i,12]<-
              lmer_bin_pup_summary[["coefficients"]][5,4] # t statistic
            timecourse_60bin_result_df_vel_dir[i,13]<-
              lmer_bin_pup_summary[["coefficients"]][5,5] # p value

            timecourse_60bin_result_df_vel_dir[i,14] <-
              ifelse(length(lmer_bin_pup_summary$optinfo$conv$lme4$message)
                                                   != 0,
                                               lmer_bin_pup_summary$optinfo$conv$lme4$message, 'pass')

     i = i+1
}
# timecourse_result_df_pos<- timecourse_result_df
View(timecourse_60bin_result_df_vel_dir)

View(timecourse_60bin_result_df_vel_dir)

timecourse_60bin_result_df_vel_dir %>%
  ggplot(aes(timebins, Estimate_ar))+
  geom_line(size = 1)+
  geom_line(aes(y = Estimate_vl), linetype = "dashed", size = 1)+
  geom_line(aes(y = Estimate_br), linetype = "dotted", size = 1)+
  geom_line(aes(y = Estimate_ar_vl), linetype = "dotdash", size = 1, color = "red")
  ylim(-.1,5)

# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
?p.adjust
timecourse_60bin_result_df_vel_dir$p_ar_adj<- p.adjust(timecourse_60bin_result_df_vel_dir$p_ar, method = "holm")
timecourse_60bin_result_df_vel_dir$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_ar_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_vel_dir$p_vl_adj <- p.adjust(timecourse_60bin_result_df_vel_dir$p_vl, method = "holm")
timecourse_60bin_result_df_vel_dir$p_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_vl_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_vel_dir$p_br_adj <- p.adjust(timecourse_60bin_result_df_vel_dir$p_br, method = "holm")
timecourse_60bin_result_df_vel_dir$p_br_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_br_adj<.05, TRUE, FALSE)

timecourse_60bin_result_df_vel_dir$p_ar_vl_adj <- p.adjust(timecourse_60bin_result_df_vel_dir$p_ar_vl, method = "holm")
timecourse_60bin_result_df_vel_dir$p_ar_vl_adj_TRUE<- if_else(timecourse_60bin_result_df_vel_dir$p_ar_vl_adj<.05, TRUE, NULL)

# find the first and last true in a sequence of TRUES
duplicated(timecourse_60bin_result_df_vel_dir$p_ar_adj_TRUE, na.rm = TRUE)

# https://masterr.org/r/how-to-find-consecutive-repeats-in-r/
timecourse_60bin_result_df_vel_dir$test<- NULL

timecourse_60bin_result_df_vel_dir$test <- rle(timecourse_60bin_result_df_vel_dir$p_ar < 0.05)
```

pupiul velocity and speed might better caprure arousal dynamics because the temporal dynamics are less adffected by a susrtauned effect of brighetenss. whereas amplitude is p[robably strongly affected by brighteness which restricts variability in input from a arousal componenets
